---
title: 'Class 11: Scraping Multiple Webpages'
author: "Fadel M Megahed"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    code_download: true
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Learning Objectives

- Enable you to scrape multiple webpages (from the same site), using a `for` loop type approach.  

- Enable you to scrape multiple webpages (from the same site), using the [purrr package](https://purrr.tidyverse.org/), which is a functional programming approach. *Note:* In this process, we will create our own function.


## Re-examining the bulletin example

Let us try to expand on the example from last class to include the following: [ACC](https://bulletin.miamioh.edu/courses-instruction/acc/), [BUS](https://bulletin.miamioh.edu/courses-instruction/bus/), [ISA](https://bulletin.miamioh.edu/courses-instruction/isa/), and [MKT](https://bulletin.miamioh.edu/courses-instruction/mkt/). 


**COMMENT:** Obviously, you can repeat your code few times with changing the URL. This will work for a few links but would be quite tedious for large amounts of scraping. We will follow the **DRY Principle**, which stands for **Don't Repeat Yourself**.


```{r bulletin}
dept_abbrv = c('acc', 'bus', 'isa', 'mkt')

courses_df = data.frame() # initializing a container to store stuff in from the loop
for (abbrv in dept_abbrv) {
  cat( rep("-", 50) , "\n" )
  print(abbrv)
  bulletin_url = paste0(
    'https://bulletin.miamioh.edu/courses-instruction/', abbrv, '/'
  )
  
  # Q: Why did Fadel make this an R object instead of a string like last class?
  # [a] we did this so we can reuse the rest of our code with only changing the URL
  webpage = rvest::read_html(bulletin_url)
  
  webpage |> rvest::html_elements("strong") |> rvest::html_text2() -> titles
  webpage |> rvest::html_elements("p.courseblockdesc") |> rvest::html_text2() -> descs
  
  df = data.frame(title = titles, desc = descs)
  print(df$title[1:2])
  courses_df = rbind(courses_df, df)
}


```


## `purrr` approach for the same problem

This is a functional programming approach, and we will write our own function. In R, we use the function called `function` to create a function. As opposed to Python, R functions return a single object. 


```{r purrr}
dept_abbrv = c('acc', 'bus', 'isa', 'mkt')

# This function takes an abbrv as an input and returns a data_frame as an output
scrape_mu_bulletin = function(abbrv){
  bulletin_url = paste0(
    'https://bulletin.miamioh.edu/courses-instruction/', abbrv, '/'
  )
  
  # Q: Why did Fadel make this an R object instead of a string like last class?
  # [a] we did this so we can reuse the rest of our code with only changing the URL
  webpage = rvest::read_html(bulletin_url)
  
  webpage |> rvest::html_elements("p.courseblocktitle") |> rvest::html_text2() -> titles
  webpage |> rvest::html_elements("p.courseblockdesc") |> rvest::html_text2() -> descs
  
  df = data.frame(title = titles, desc = descs)
  return(df)
}

test = scrape_mu_bulletin(abbrv = 'eco')

# to use functions from purrr, we will use a map_*(), or map2_*(), or a pmap_*()
# map uses a function that takes a single input (or you are only changing a single input)
# map2 uses a function that takes two inputs
# pmap >=3
# after the _, you put the type of object you are getting back

# the .x is the vector that we will iterate over
# and the .f is the function we use

courses_df_from_purrr = purrr::map_df(.x = dept_abbrv, .f = scrape_mu_bulletin)
```


## Scrape data from the website planecrashinfo

The website that we want to scrape is called: <https://www.planecrashinfo.com/> and it contains a database of plane crashes by year.


```{r}
year = 2025

crash_url = paste0('https://www.planecrashinfo.com/', year, '/', year, '.htm')

crash_page <- rvest::read_html(crash_url, encoding = "ISO-8859-1")

# This should now print without the error
crash_page

# How many <table> elements are on the page?
crash_tables <- crash_page |>
  rvest::html_elements("table") |>
  rvest::html_table()

# From a cleaning perspective:
# [1] Obviously, translate this into a DF instead of a list
# [2] To replace the current headers with row 1 and then delete row 1
# [3] Convert Date into a date column instead of chr
# [4] More complex cleaning to split multiple information within a cell into separate columns (outside of the scope of today's class -- feel free to try AI or regular expressions if you are in 414)

# back to our pepper shaker analogy
crash_df = crash_tables[[1]] # subsetting a list

colnames(crash_df) = c(crash_df$X1[1], crash_df$X2[1], crash_df$X3[1], crash_df$X4[1])
crash_df = crash_df[-1, ]

# convert Date column into a date type obj
crash_df = crash_df |> 
  dplyr::mutate(Date = lubridate::dmy(Date))

dplyr::glimpse(crash_df)
```



## Game

```{r game}
page = rvest::read_html("https://isa401-salvage.vercel.app/registry?start=1")
classes = page |>
  rvest::html_elements(".Dreadnought") |>
  rvest::html_text2()
length(classes)   # check this first: 


base = "https://isa401-salvage.vercel.app"
starts = seq(from = 1, to = 351, by = 50) # c(1, 51, 101, 151, 201, 251, 301, 351)
pages = vector("list", length(starts)) # initializing the list [similar to initializing the df]
for (i in seq_along(starts)) {
  pg = rvest::read_html(paste0(base, "/registry?start=", starts[i]))
  pages[[i]] = data.frame(
    class = pg |> rvest::html_elements("div > ul > li:nth-child(1) > span") |> 
      rvest::html_text2(),
    value = pg |> rvest::html_elements("div > ul > li:nth-child(3) > span") |> 
      rvest::html_text2() |> readr::parse_number()
  )
  Sys.sleep(1)   # robots.txt asks for it
}
registry = dplyr::bind_rows(pages)   # 400 rows?

dreadnought_df = registry |> 
  dplyr::filter(class == "Dreadnought")

sum(dreadnought_df$value)

```










